Graph-Based Neural Reconstruction from Skeletonized 3D Networks

### 2018-03-05 papers/eccv2018/0_introduction.tex
paper: major changes to abstract, intro, and related works

\begin{figure}[t]
	\subfloat[]{
	\includegraphics[width=.47\linewidth]{figures/schema/pre-multicut-with-arrows.pdf}
	}
	\subfloat[]{
	\includegraphics[width=.47\linewidth]{figures/schema/post-multicut.png}
	}
	\caption{Example improvement of neural reconstruction. (a) We extract 3D skeletons from pixel-based segmentation algorithms to create a 3D graph representation. Edges with high segmentation error probabilities are indicated by the red arrows. (b) We improve the segmentation accuracy using a graph partitioning algorithm, leveraging both local and global information.}
	\label{fig:teaser}
\end{figure}

%\donglai{usually, top-down means split.. but we are also bottom-up, but with different representation}
The field of connectomics is concerned with reconstructing the wiring diagram of the brain at nanometer resolutions to enable new insights into the workings of the brain~\cite{haehn2017scalable,kasthuri2015saturated}. Recent advancements in image acquisition using multi-beam serial-section electron microscopy (sSEM) have allowed researchers to produce terabytes of image data every hour~\cite{hildebrand2017whole}. It is not feasible for domain experts to manually reconstruct this vast amount of image data~\cite{haehn2014design}. State-of-the-art automatic reconstruction approaches use pixel-based segmentation with convolutional neural networks (CNNs) followed by agglomeration strategies~\cite{seymour2016rhoananet,lee2015recursive,nunez2014graph,parag2017anisotropic,ronneberger2015u,zlateski2015image}.
These \textit{bottom-up pixel-based} methods produce excellent results but still fall short of acceptable error rates for large volumes.

%\begin{figure*}[t]
%	\centering
%	\subfloat[]{
%	\includegraphics[width=.24\linewidth]{./figures/pipeline/image.png}
%	}
%	\subfloat[]{
%	\includegraphics[width=.24\linewidth]{./figures/pipeline/affinities.png}
%	}
%	\subfloat[]{
%	\includegraphics[width=.24\linewidth]{./figures/pipeline/watershed.png}
%	}
%	\subfloat[]{
%	\includegraphics[width=.24\linewidth]{./figures/pipeline/neuroproof.png}
%	}
%	\caption{An overview of a pixel-based connectomics segmentation pipeline. (a) Original EM image data (b) Output of a CNN predicting voxel affinities (c) Clustering of the affinities using a watershed algorithm (d) Agglomeration of the super-voxels into larger segments.}
%	\label{fig:pipeline}
%\end{figure*}

%
%\begin{figure*}[t!]
%	\centering
%	(a) \includegraphics[width=0.18\linewidth]{./figures/pipeline/image.png}
%	\hspace{0.025\linewidth}
%	(b) \includegraphics[width=0.18\linewidth]{./figures/pipeline/affinities.png}
%	\hspace{0.025\linewidth}
%	(c) \includegraphics[width=0.18\linewidth]{./figures/pipeline/watershed.png}
%	\hspace{0.025\linewidth}
%	(d) \includegraphics[width=0.18\linewidth]{./figures/pipeline/neuroproof.png}
%	\caption{An overview of a pixel-based connectomics segmentation pipeline. (a) Original EM image data (b) Output of a CNN predicting voxel affinities (c) Clustering of the affinities using a watershed algorithm (d) Agglomeration of the super-voxels into larger segments.}
%	\label{fig:pipeline}
%\end{figure*}
%
%Researchers address the failures of these pixel-based algorithms by training random-forest classifiers to agglomerate an oversegmentation of voxels~\cite{nunez2014graph,10.1371/journal.pone.0125825}.
%These classifiers take the output of the pixel-based algorithms as input and generate high-level statistics such as affinity distributions between regions.
%Presently, these methods use hand-designed features despite the evidence that machine-learned features perform better~\cite{bogovic2013learned}.
%These \textit{region-based} algorithms outperform the pixel-based algorithms but do not provide the accuracy needed for large scale reconstructions of the brain.

%Here we introduce a scalable, top-down segmentation algorithm that also leverages local information.
%Partitioning globally allows us to apply domain-specific constraints to the segmentation task.
%We extract a graph representation from the input segmentation.
%By simplifying the 3-D segments by their skeletons, we can quickly generate the graph nodes and edges.

We present a \textit{top-down graph-based} method that builds on the outputs of bottom-up pixel-based segmentation approaches. We first extract 3D skeleton networks from the input segmentation and generate a simplified 3D graph (Fig.~\ref{fig:teaser}a). We train a CNN classifier on the agglomerated regions in the segmentation data to detect errors. We run the classifier to populate the graph edge weights with error probabilities. We then use a graph optimization algorithm to partition the graph into the final improved reconstruction by enforcing domain-specific global constraints from biology (Fig.~\ref{fig:teaser}b).

Our approach operates at a level of abstraction above existing pixel-based methods. This allows us to leverage both local and global information to produce more accurate reconstructions. Our method is independent of image resolution and acquisition parameters, enabling its application to isotropic and anisotropic image data without retraining. Using the 3D graph induced by the segmentation allows us to enforce global biological constraints on the reconstruction. Our dual approach of assessing local decisions in a global context yields accuracy improvements over existing reconstruction methods.

This work makes the following contributions: (1) a novel top-down method using  graphs from skeletonized 3D networks for improved neural reconstruction of connectomics data; (2) a region-based CNN classifier to detect errors using the 3D graph as global constraint; (3) an empirical evaluation of our method on several connectomics datasets; (4) our method yields improved performance over a state-of-the-art pixel-based reconstruction approach on average by 19.3\% without drastically increasing the running time.

>>>>

\begin{figure}[t]
	\subfloat[]{
	\includegraphics[width=.47\linewidth]{figures/schema/pre-multicut-with-arrows.pdf}
	}
	\subfloat[]{
	\includegraphics[width=.47\linewidth]{figures/schema/post-multicut.png}
	}
	\caption{Example improvement of neural reconstruction. (a) We extract 3D skeletons from pixel-based segmentation algorithms to create a graph representation. Red arrows highlight errors in the input segmentation. (b) We improve the segmentation accuracy using a graph partitioning algorithm, leveraging both local and global information.}
	\label{fig:teaser}
\end{figure}

The field of connectomics is concerned with reconstructing the wiring diagram of the brain at nanometer resolutions to enable new insights into the workings of the brain~\cite{haehn2017scalable,kasthuri2015saturated}. 
Recent advancements in image acquisition using multi-beam serial-section electron microscopy (sSEM) allow researchers to produce terabytes of image data per hour~\cite{hildebrand2017whole}. 
It is infeasible for domain experts to manually reconstruct this vast amount of image data~\cite{haehn2014design}. 
State-of-the-art automatic reconstruction approaches use pixel-based segmentation with convolutional neural networks (CNNs) followed by agglomeration strategies~\cite{seymour2016rhoananet,lee2015recursive,nunez2014graph,parag2017anisotropic,ronneberger2015u,zlateski2015image}.
These \textit{bottom-up pixel-based} methods produce excellent results but still fall short of acceptable error rates for large volumes.

We present a \textit{global\TODO{?} graph-based} method that builds on the outputs of bottom-up pixel-based segmentation approaches. 
We first extract skeletons from labels in the input segmentation and generate a simplified graph (Fig.~\ref{fig:teaser}a). 
Next, a trained CNN classifier detects split errors in the segmentation data. 
Split errors correspond to neurons which are incorrectly segmented with multiple labels. 
This classifier produces probabilities that two segments belong to the same neuron.
These probabilities correspond to edge weights in our graph extracted from the input segmentation.
We then use a graph optimization algorithm to partition the graph into a final improved reconstruction by enforcing domain-specific global constraints from biology (Fig.~\ref{fig:teaser}b).

Our approach operates at a level of abstraction above existing pixel-based methods. 
This allows us to leverage both local and global information to produce more accurate reconstructions. 
Our method is independent of image resolution and acquisition parameters, enabling its application to isotropic and anisotropic image data without retraining.
Images generated by electron microscopes often differ in appearance because of variations in staining techniques \cite{briggman2012volume}.
By removing the dependence of our algorithm on the input images, we greatly reduce the need for additional costly ground truth data for each new stack of images.
Using the graph induced by the segmentation allows us to enforce global biological constraints on the reconstruction. 
Our dual approach of assessing local decisions in a global context yields accuracy improvements over existing reconstruction methods.

This work makes the following contributions: (1) a novel top-down\TODO{?} framework that extracts graphs from skeletonized 3D networks for improved neural reconstruction of connectomics data; (2) a region-based CNN classifier to detect errors; (3) an empirical evaluation of our method on several connectomics datasets; (4) improved performance over a state-of-the-art pixel-based reconstruction approach on average by \TODO{XX}\% with suitable running times.

### 2018-03-05 papers/eccv2018/1_related_work.tex
paper: major changes to abstract, intro, and related works

We review some of the most successful segmentation methods that have been applied to large-scale EM images in connectomics.
%Fig.~\ref{fig:pipeline} shows the results of a typical connectomics segmentation pipeline.

\paragraph{Pixel-based methods.}
A large amount of connectomics research considers the problem of extracting segmentation information at the pixel (i.e., voxel) level from the raw EM images. Some early techniques apply computationally expensive graph partitioning algorithms with a single node per pixel~\cite{andres2012globally}. However, these methods do not scale to terabyte datasets. More recent methods train classifiers to predict membrane probabilities per image slice either using 2D~\cite{ciresan2012deep,jain2010boundary,kaynig2015large,seymour2016rhoananet,amelio_segmentation} or 3D CNNs~\cite{lee2015recursive,ronneberger2015u,turaga2010convolutional}.

Oftentimes these networks produce probabilities for the affinity between two voxels (i.e., the probability that adjacent voxels belong to the same neuron). The MALIS cost function is specifically designed for generating affinities that produce good segmentations~\cite{briggman2009maximin}. More recently, flood-filling networks produce segmentations by training an end-to-end neural network that goes from EM images directly to label volumes~\cite{januszewski2016flood}. These networks produce impressive accuracies but at a high computational cost.

\paragraph{Region-based methods.}
%Lately, many recent advancements in segmentation use artificial neural networks since machine-learned features outperform hand-designed ones~\cite{bogovic2013learned}.
%A significant amount of research focuses on the training and optimization of these deep neural networks~\cite{chatfield2014return,maas2013rectifier,nesterov1983method}.
Several pixel-based approaches generate probabilities that neighboring pixels belong to the same neuron.
Often a watershed algorithm will then cluster pixels into super-pixels~\cite{zlateski2015image}.
Many methods build on top of these region-based strategies and train random-forest classifiers to produce the final segmentations~\cite{seymour2016rhoananet,nunez2014graph,10.1371/journal.pone.0125825,parag2017anisotropic,zlateski2015image}.

\paragraph{Error-correction methods.}
Some recent research builds on top of these region-based methods to correct errors in the segmentation either using human proofreading~\cite{haehn2017guided,haehn2014design,mojo2} or fully automatically~\cite{rolnick2017morphological,error_correction_using_CNN}.
However, to our knowledge, our method is the first to extract a 3D graph from pixel-based segmentations for a true top-down error correction approach. This allows us to enforce domain-specific biology constraints and use efficient graph partitioning algorithms. Many segmentation and clustering algorithms use graph partitioning techniques~\cite{andres2012globally} or normalized cuts for traditional image segmentation~\cite{kappes2016higher,shi2000normalized,tatiraju2008image}.
Even though graph partitioning is an NP-Hard problem~\cite{demaine2006correlation} there are several useful multicut heuristics that provide good approximations with reasonable computational costs~\cite{horvnakova2017analysis}. We use the method of Keuper et al.~\cite{keuper2015efficient} to partition the extracted 3D graph into the final neural reconstruction.

>>>>

\paragraph{Pixel-based methods.}
A significant amount of connectomics research considers the problem of extracting segmentation information at the pixel (i.e., voxel) level from the raw EM images. 
Some methods use a random forest populated with hand-designed features based on image characteristics around a given pixel to predict membrane probabilities~\cite{kaynig2015large}.
Most recent advancements use convolutional neural networks since machine-learned features outperform hand-designed ones~\cite{bogovic2013learned}.
Originally, networks predicted membrane probabilities per each image slice using 2D convolutions~\cite{seymour2016rhoananet,ronneberger2015u,ciresan2012deep,jain2010boundary,kaynig2015large,amelio_segmentation}.
However, recent research extends these convolutions to include the z-dimension improving performance~\cite{lee2015recursive,parag2017anisotropic,cciccek20163d,turaga2010convolutional}.
Many of these networks produce probabilities for the affinity between two voxels (i.e., the probability that adjacent voxels belong to the same neuron). 
The MALIS cost function is specifically designed for generating affinities that produce good segmentations~\cite{briggman2009maximin}. 
More recently, flood-filling networks produce segmentations by training an end-to-end neural network that goes from EM images directly to label volumes~\cite{januszewski2016flood}. 
These networks produce impressive accuracies but at a high computational cost.
Data augmentation in both training and testing can increase the prediction accuracy in boundary detection~\cite{zeng2017deepem3d}.
Lee et al. surpass the estimated human accuracy on the SNEMI3D dataset with a variant of the 3D U-Net architecture~\cite{lee2017superhuman}.

\paragraph{Region-based methods.}

Some early techniques apply computationally expensive graph partitioning algorithms with a single node per superpixel~\cite{andres2012globally}. 
Several pixel-based approaches generate probabilities that neighboring pixels belong to the same neuron.
Often a watershed algorithm will then cluster pixels into super-pixels~\cite{zlateski2015image}.
Many methods build on top of these region-based strategies and train random-forest classifiers to produce the final segmentations~\cite{seymour2016rhoananet,nunez2014graph,parag2017anisotropic,zlateski2015image,10.1371/journal.pone.0125825}.
Some methods rely solely on the accuracy of the predicted affinities and agglomerate hierarchically based on the mean affinity between supervoxels~\cite{lee2017superhuman,funke2017deep}.
Pape et al. present a scalable multicut algorithm to partition superpixels~\cite{beier2017multicut}.

\paragraph{Error-correction methods.}
Additional research builds on top of these region-based methods to correct errors in the segmentation either using human proofreading~\cite{haehn2014design,haehn2017guided,mojo2} or automatic methods~\cite{rolnick2017morphological,error_correction_using_CNN}.
However, to our knowledge, our method is the first to extract a 3D graph from an input segmentation for a true top-down\TODO{?} error correction approach. 
This allows us to enforce domain-specific biology constraints and use efficient graph partitioning algorithms. 
Many segmentation and clustering algorithms use graph partitioning techniques~\cite{andres2012globally} or normalized cuts for traditional image segmentation~\cite{kappes2016higher,shi2000normalized,tatiraju2008image}.
Even though graph partitioning is an NP-Hard problem~\cite{demaine2006correlation} there are several useful multicut heuristics that provide good approximations with reasonable computational costs~\cite{horvnakova2017analysis}. 
We use the method of Keuper et al.~\cite{keuper2015efficient} to partition the extracted graph into the final neural reconstruction.

### 2018-03-05 papers/eccv2018/2_method.tex
paper: major changes to abstract, intro, and related works

\begin{figure*}[htbp]
	\begin{center}
		\includegraphics[width=0.24\linewidth]{./figures/methods/multicut_input.png}
		\includegraphics[width=0.24\linewidth]{./figures/methods/pre-multicut.png}
		\includegraphics[width=0.24\linewidth]{./figures/methods/multicut-graph.png}
		\includegraphics[width=0.24\linewidth]{./figures/methods/post-multicut.png}
	\end{center}
	\caption{Outline of our approach, from left to right: result of the pixel-based segmentation and agglomeration algorithm; segments of several selected neurons from the initial segmentation; extracted skeletonized 3D network of those segments; improved 3D reconstruction of the selected segments after graph construction and partitioning with constraints.}
	\label{fig:overview}
\end{figure*}

>>>>

\begin{figure*}[htbp]
	\begin{center}
		\subfloat[]{\includegraphics[width=0.24\linewidth]{./figures/methods/multicut_input.png}}
		\subfloat[]{\includegraphics[width=0.24\linewidth]{./figures/methods/pre-multicut.png}}
		\subfloat[]{\includegraphics[width=0.24\linewidth]{./figures/methods/multicut-graph.png}}
		\subfloat[]{\includegraphics[width=0.24\linewidth]{./figures/methods/post-multicut.png}}
	\end{center}
	\caption{Outline of our approach, from left to right: result of the pixel-based segmentation and agglomeration algorithm; segments of several neurons from the initial segmentation; extracted skeletonized network of those segments; improved 3D reconstruction of the selected segments after graph construction and partitioning with constraints.}
	\label{fig:overview}
\end{figure*}

### 2018-03-05 papers/eccv2018/paper.tex
paper: added information on augmentations/lifted multicut
paper: major changes to abstract, intro, and related works

\begin{document}
% \renewcommand\thelinenumber{\color[rgb]{0.2,0.5,0.8}\normalfont\sffamily\scriptsize\arabic{linenumber}\color[rgb]{0,0,0}}
% \renewcommand\makeLineNumber {\hss\thelinenumber\ \hspace{6mm} \rlap{\hskip\textwidth\ \hspace{6.5mm}\thelinenumber}}
% \linenumbers
\pagestyle{headings}
\mainmatter
\def\ECCV18SubNumber{***}  % Insert your submission number here

@@

\authorrunning{ECCV-18 submission ID \ECCV18SubNumber}

\title{Graph-Based Neural Reconstruction from Skeletonized 3D Networks}

@@

@@

\begin{abstract}
Advancements in electron microscopy image acquisition have created massive connectomics datasets in the terabyte range that make manual reconstruction of neuronal structures infeasible.
Current state-of-the-art automatic methods segment neural membranes at the pixel level followed by agglomeration methods to create full neuron reconstructions.
However, these approaches widely neglect global geometric properties that are inherent in the graph structure of neural wiring diagrams.
In this work, we follow bottom-up pixel-based reconstruction by a top-down graph-based method to more accurately approximate neural pathways.
We first generate skeletons in 3D from the neuron labels of the pixel-based segmentation.
We then simplify this skeletonized 3D network into a 3D graph with nodes corresponding to labels from the segmentation and edges identifying potential locations of segmentation errors.
We use a CNN classifier trained on ground truth data to generate edge weights on the 3D graph corresponding to error probabilities.
We then apply a multicut algorithm to generate a partition on the graph that improves the final segmentation.
Because the 3D graph is small and encodes top-down information our method is efficient and globally improves the neural reconstruction.
We demonstrate the performance of our approach on multiple real-world connectomics datasets with an average split variation of information improvement of 19.3\%.
\keywords{connectomics, skeletonization, deep learning}
\end{abstract}

>>>>

\begin{document}
% \renewcommand\thelinenumber{\color[rgb]{0.2,0.5,0.8}\normalfont\sffamily\scriptsize\arabic{linenumber}\color[rgb]{0,0,0}}
% \renewcommand\makeLineNumber {\hss\thelinenumber\ \hspace{6mm} \rlap{\hskip\textwidth\ \hspace{6.5mm}\thelinenumber}}
% \linenumbers
\pagestyle{headings}
\mainmatter
\def\ECCV18SubNumber{534}  % Insert your submission number here

@@

\authorrunning{ECCV-18 submission ID \ECCV18SubNumber}
\title{Graph-Based Neural Reconstruction from Skeletonized 3D Networks}

@@

\newcommand\TODO[1]{\textcolor{red}{#1}}

@@

\begin{abstract}
Advancements in electron microscopy image acquisition have created connectomics datasets terabytes in size making manual reconstruction of neuronal structures infeasible.
Current state-of-the-art automatic methods classify neural membranes at the pixel level followed by agglomeration methods to create full neuron reconstructions.
However, these approaches widely neglect global geometric properties that are inherent in the graph structure of neural wiring diagrams.
In this work, we follow pixel-based reconstruction by a global graph-based method to more accurately approximate neural pathways.
We first generate skeletons in 3D from the neuron labels of the pixel-based segmentation.
Next, we simplify this skeletonized 3D network into a graph with nodes corresponding to labels from the segmentation and edges identifying potential locations of split errors.
A CNN classifier produces edge weights for the graph corresponding to the probability of error. 
We formulate the graph into a multicut partitioning problem to improve the final segmentation.
Since the 3D graph is small and encodes top-down information our method is efficient and globally improves the neural reconstruction.
We demonstrate the performance of our approach on multiple real-world connectomics datasets with an average split variation of information improvement of \TODO{XX}\%.
\keywords{connectomics, skeletonization, deep learning}
\end{abstract}
